Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
Added \small to captions

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{henry}
    \caption{Henry teaching Nao how to write numbers, with the help of an
    occupational therapist.}
    \label{fig:henry}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{experimental_setup}
    \caption{Our experimental setup: face-to-face interaction with a Nao robot.
    The robot writes on the tactile tablet, the child then corrects the robot by
    directly overwriting its letters on the tablet, with a stylus directly. An adult
    (either a therapist or an experimenter, depending on the studies), remains next
    to the child to guide the work (prompting, turn taking, etc.). For some studies, a second tablet and an additional camera (dashed) are employed.}
    \label{experimental_setup}
\end{figure}

@@

\begin{figure}[thpb]
     \begin{center}
            \includegraphics[width=0.7\linewidth]{naoWriting2.png}
    \end{center}
    \caption{A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.}%

@@

\begin{table}[ht!]
\centering
\caption{Field studies conducted within the project}
\label{studies}
\begin{tabular}{@{}lp{4.5cm}p{2.2cm}p{2.5cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Diego}     & Case-study, spanning over 4 weeks              & 1.5 hours $\times$ 4 weeks & 1                                     & 5          \\
{\it Haut-Lac}  & Pair (with turn-taking) interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Henry}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[height=3.9cm]{schools}
    \includegraphics[height=3.9cm]{schools2}
    \caption{The first field studies were focused on technical validation, with
    above 70 pupils interacting with the robot over short periods (around 15
minutes), either alone or in small groups.}
    \label{fig:schools}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{diego}
    \caption{Diego working with Nao}
    \label{fig:diego}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{abc-writer}
    \caption{Screenshot of the Android application developed to be used as
    pre-test and post-test: the child must follow with his finger the path of
the letter or number. We count the number of times the finger goes outside of
the red-bordered area.}
    \label{}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demomstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{henry_demos}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_distances}
    \caption{Two metrics to assess the handwriting progresses: Euclidian
    distance in the Eigenspace of the number dataset (top figure) or in
cartesian space (bottom figure). Green lines represent the robot performance,
blue lines Henry's performance. The round IDs correspond to the demonstrations
pictured on Figure~\ref{henry_demos}.}
    \label{henry_distances}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{henry}
    \caption{\small Henry teaching Nao how to write numbers, with the help of an
    occupational therapist.}
    \label{fig:henry}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{experimental_setup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc nao} robot.
        The robot writes on the tactile tablet, the child then corrects the
        robot by directly overwriting its letters on the tablet, with a stylus
        directly. An adult (either a therapist or an experimenter, depending on
        the studies), remains next to the child to guide the work (prompting,
        turn taking, etc.). For some studies, a second tablet and an additional
        camera (dashed) are employed.}

    \label{experimental_setup}
\end{figure}

@@

\begin{figure}[thpb]
     \begin{center}
            \includegraphics[width=0.7\linewidth]{naoWriting2.png}
    \end{center}
    \caption{\small A demonstration of the robot simulating the writing of a word with
    its finger. The motion of the robot is synchronised with the display of the
    tablet, communicating over ROS.}%

@@

\begin{table}[ht!]
\centering
\caption{\small Field studies conducted within the project}
\label{studies}
\begin{tabular}{@{}lp{4.5cm}p{2.2cm}p{2.5cm}l@{}}
\toprule
{\bf Study}     & {\bf Type}                                    & {\bf Duration}              & {\bf Children \#}                     & {\bf Ages} \\ \midrule
{\it ISG 1}     & Unstructured group interaction at school      & 16 min/group               & 4 $\times$ 8 children                 & 6-7        \\
{\it Florimont} & Individual/Pair interaction at school         & 11 min/group               & 7 (individual) + 7 $\times$ 2 (pairs) & 7-8        \\
{\it Diego}     & Case-study, spanning over 4 weeks              & 1.5 hours $\times$ 4 weeks & 1                                     & 5          \\
{\it Haut-Lac}  & Pair (with turn-taking) interaction at school & 26 min/group                            & 7 $\times$ 2                          & 5-6        \\
{\it ISG 2}     & Individual interaction at school              & 18 min                            & 6                                     & 5-6        \\
{\it Henry}     & Case-study, spanning over 4 weeks              & 1h $\times$ 4 weeks        & 1                                     & 5          \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[height=3.9cm]{schools}
    \includegraphics[height=3.9cm]{schools2}
    \caption{\small The first field studies were focused on technical validation, with
    above 70 pupils interacting with the robot over short periods (around 15
minutes), either alone or in small groups.}
    \label{fig:schools}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{diego}
    \caption{\small Diego working with Nao}
    \label{fig:diego}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{abc-writer}
    \caption{\small Screenshot of the Android application developed to be used as
    pre-test and post-test: the child must follow with his finger the path of
the letter or number. We count the number of times the finger goes outside of
the red-bordered area.}
    \label{}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{\small Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demomstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{henry_demos}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_distances}
    \caption{\small Two metrics to assess the handwriting progresses: Euclidian
    distance in the Eigenspace of the number dataset (top figure) or in
cartesian space (bottom figure). Green lines represent the robot performance,
blue lines Henry's performance. The round IDs correspond to the demonstrations
pictured on Figure~\ref{henry_demos}.}
    \label{henry_distances}
\end{figure}
